---
title: "Contract Renewal Statement"
output: github_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
library(tidyverse)
library(ggbump)
```

## Introduction

- I was granted one year towards tenure when I was hired in 2018. I will refer to relevant activities and achievements from my time at Husson University within the College Science and Humanities.

Empowering others to do "cool things"

- Teaching
  - Help others find what does or does not interest them 
- Scholarly activity
  - How I find my interest
- Service
  - Provide/create spaces where others can explore their interests

## Teaching

- In graduate school while I was a teaching assistant and later a faculty specialist charged with coordinating one of our introductory statistics courses, consistency of material and examinations across multiple sections was vital as many of us had very limited teaching experience. Consistent lecture slides and automatically graded homework assignments and exams helped me to focus on becoming more comfortable talking in front of people and build connections with students, but it also afford me time to develop clarifying activities (*examples of STAT2160 slides/homework*?). At times, these lecture slides/homework seemed too mechanical to me.
- While an assistant professor at Husson Univeristy, I began to transition away from lecture-driven material delievery to using guided/active lecture notes (*examples of MS132 activities*). I wanted to become more of a trail guide to students rather than the *keeper of knowledge* - I didn't have all the answers and I could help them figure it out. I read the revised 2005 GAISE report[^GAISE2005] in graduate school and was trying to integrate the six recommendations to the best of my ability (though, admittedly, focusing two of these recommendations: using real data and fostering active learning).

[^GAISE2005]: Aliaga, M., Cobb, G., Cuff, C., Garfield, J., Gould, R., Lock, R., Moore, T., Rossman, A., Stephenson, B., Utts, J., Velleman, P., Witmer, J. (2005). Guidelines for Assessment and Instruction in Statistics Education (GAISE) College Report. American Statistical Association. Online at: https://www.amstat.org/asa/files/pdfs/GAISE/2005GaiseCollege_Full.pdf

- Took part in a Faculty Learning Community facilitated by Drs. John Gabrosek and Neal Rogness on Team-Based Learning (TBL) while I was a visiting professor during the Winter 2018 semester. TBL is a type of flipped classroom experience where students do readings and watch videos outside of class, take an in-class quiz over the foundational knowledge they were asked to prepare, then class time is spend working on activities that extend their foundational understanding. Students are placed into semester long teams for where they work with each other to complete a team quiz and the in-class activities. This approach felt like a natural progression from my guided notes to me taking more of a trail guide role in students' learning.
- Worked with Dr. Rogness to restructure Dr. Gabrosek's first attempt at using TBL in STA 216 (Intermediate Applied Statistics). Gained emense insight into how to prepare active learning materials and questions to ask as activities and assessments are being designed. I really enjoyed this collaborative lesson planning because it made me more aware of my own blind-spots (what things am I not aware of because it has become second nature) (*examples of STA216 TBL activites*). Talk about collaborative lesson planning ideas from [The Carpentries](https://software-carpentry.org/lessons/) and [Teach Tech Together](http://teachtogether.tech/#s:process-maintainability).

- Transition to mastery-based (or specification or standards-based) grading (**define**) has allowed me to maintain high standards and gives students multiple opportunities to achieve the level of mastery that they are seeking. Like a traditional grading system, students are presented with overall course learning objectives. However, in a mastery-based grading system, each assessment tasks also has clearly labeled learning objectives attached to it. In these assessments, students receive substantial feedback and an indication of where they are currently (e.g., I use a rubric for each task in my [STA 418/518 grading policy](https://sta518.github.io/courses/assessment/grading/)). Unlike most traditional grading systems, students are then provided with opportunities to revise and resubmit most assessment tasks sometimes requiring students to submit additional materials like additional task items or a reflection on how the feedback aided their understanding (e.g., [STA 418/518 revision and reassement policy](https://sta518.github.io/courses/assessment/revision/)). 
- One of my departmental mentors, Dr. John Gabrosek, introduced me to Dr. John Golden from the Department of Mathematics to discuss how he does various creative activities. After our initial conversation, I invited Dr. Golden and his colleagues that also use a mastery-based grading system (i.e., Drs. David Clark, Jon Hasenbank, Lauren Keough, and Taylor Short) to hold a panel discussion with our department (*include shared google doc from this discussion?*).

- Encourage students to explore on their own. Recently I have realized that many may have never wanted to do this or had experience with self-exploration, so they need additional guidance along this process.
- How can we help students to become self-motivated?
- I am trying to be more intentional in the directions provided to students so details are presented in a concise, clear way; being cautious of the jargon I use and aware of my own blind-spots.

- Flipped-style classroom where I provide students with readings, tutorials, videos to complete outside of class. Class time is then spent working on activities (frequently in groups) or working on extending their abilities with application tasks. Sometimes these applictions have a "choose your own adventure" qualtity where students can pick a couple of items from a larger list to complete (e.g., STA 418/518). I like the ability to "roam" the classroom and work on a more personal level with groups of students and doing full class discussions/lectures when needed to clarify confusing concepts. Using materials developed by Drs. Gabrosek and Rogness in STA 215 and STA 216 have immensly aided in this process.

- Give example of STA 418/518 module prep
  - Outcomes
  - Concept map
  - Readings/tutorials
  - Activity
  - Application
  - Project

Developed activities can sometime reduce the flexibility of and improvisation of a lecture-based classroom; however, clarifying lectures or discussion can still be sprinkled throughout to fit the class' needs.

In our transition to remote and online learning during the second half of  Winter 2020 and more specifically Spring/Summer 2020, I began using scheduled classtime as more of a live demonstration rather than working on activities where students could add items to my agenda that they wanted me to have prepared up to a couple of hours prior to class time. They could still ask questions live if new ones arose or they did not have the opportunity to add items before I closed that day's agenda (**refer to examples on GitHub**). These sessions were recorded so students that were not able to actively participate could still view the session.

Agenda/reminders

Directions (especially on at-home assignments) have become more detailed

Organized Bb course site. This isn't always the most evident to me and I ask for student feedback as the semester progresses. Responsive to needs of students and use verbal feedback to adapt Bb.

Midterm evaluation process. How is this evolving? How do I use this and share with students? (*Show process of Google Form > RMarkdown > Report*)

Peer Feedback forms (*Show process*). How is this evolving? How can I get more student involvement in their evaluations? Could be a learning journal entry.

Students' learning journals on GitHub. Can give additional feedback or reinforce their understanding (*show anonymized examples from Spring 2020 STA 418/518*)

Themes from LIFT evaluations. Do I still have my evaluations from Husson?

Colors are consistent from between bump plots below. However, these colors are simply used to help make changes across sections more clear.
Items that were repeatedly lower in rank are shaded darker in color.
Overall, students' seem to feel that I am *at least* "good" in these formative items, but there are some places that I have tried to improve based on their ratings and comments.

In lower-division courses, I need to do a better job of making the course content more relevant to students.
One thing I do differently in the upper-division courses it to incorporate more of project-based assessments (even in smaller homework assignments).
Students regardless of course level appear to notice my enthusiasm for the material and I might be able to better use this trait to help students in these lower-division course see the relevance of the material.
For example, I could do a better job setting up activities to help students.

```{r sta215-bump, cache = TRUE}

sta215_formative_items <- tribble(
  ~Item,	~W19,	~S19,	~F19,
"Course Organization was:",	3,	6,	3,
"Explanations by instructor were:",	6,	7,	14,
"Instructor's ability to present alternative explanations when needed was:",	2,	8,	13,
"Instructor's use of examples and illustrations was:",	8,	13,	4,
"Quality of questions or problems raised by the instructor was:",	7,	15,	9,
"Student confidence in instructor's knowledge was:",	10,	2,	6,
"Instructor's enthusiasm was:",	1,	1,	2,
"Encouragement given students to express themselves was:",	11,	16,	15,
"Answers to student questions were:",	12,	11,	10,
"Availability of extra help when needed was:",	16,	9,	5,
"Use of class time was:",	13,	5,	16,
"Instructor's interest in whether students learned was:",	14,	3,	7,
"Amount you learned in the course was:",	4,	14,	12,
"Relevance and usefulness of course content were:",	17,	17,	17,
"Evaluative and grading techniques (test, papers, projects, etc.) were:",	15,	10,	8,
"Reasonableness of assigned work was:",	9,	12,	11,
"Clarity of student responsibilities and requirements was:",	5,	4,	1,
)

sta215_formative_items <- sta215_formative_items %>% 
  mutate(blank = NA)

sta215_formative_items_long <- sta215_formative_items %>% 
  mutate(Item = factor(Item, levels = sta215_formative_items$Item)) %>% 
  pivot_longer(cols = -Item, names_to = "Semester", values_to = "Ranking") %>% 
  mutate(Semester = factor(Semester, levels = c("W19", "S19", "F19")),
         Bottom = if_else(Ranking > 10, "Yes", "No"))


sta215_formative_items_long %>%
  ggplot(aes(x = as.numeric(Semester), y = Ranking, group = Item, color = Item, label = Item)) +
  geom_bump(size = 2, alpha = 0.3) +
  scale_y_reverse(breaks = 1:17, labels = 1:17) +
  geom_bump(data = sta215_formative_items_long %>% filter(Ranking > 10),
            aes(x = as.numeric(Semester), y = Ranking, group = Item, color = Item),
            size = 2, inherit.aes = FALSE) +
  geom_text(sta215_formative_items_long %>% filter(Semester == "F19"), 
            mapping = aes(x = as.numeric(Semester) + 0.1, y = Ranking), hjust = 0) +
  scale_x_continuous(breaks = 1:(length(levels(sta215_formative_items_long$Semester))+1),
                     labels = c(levels(sta215_formative_items_long$Semester),""),
                     expand = c(0,0.05),
                     limits = c(1, 12)) +
  theme_classic() + 
  labs(x = "Semester",
       y = "Relative Ranking",
       title = "Formative Items",
       subtitle = "STA 215") +
  theme(legend.position = "none")

# sta215_formative_items_long %>% 
#   ggplot(aes(x = as.numeric(Semester), y = Ranking, group = Item, label = Item, color = Bottom)) + 
#   geom_line() +
#   geom_text(sta215_formative_items_long %>% filter(Semester == "F19"), 
#             mapping = aes(x = as.numeric(Semester) + 0.1, y = Ranking), hjust = 0) +
#   scale_x_continuous(breaks = 1:4,
#                      labels = c(levels(sta215_formative_items_long$Semester),""),
#                      expand = c(0,0.05),
#                      limits = c(1, 12)) +
#   scale_y_continuous(breaks = -1:-17,
#                      labels = 1:17) +
#   scale_y_reverse() +
#   theme_classic() + 
#   labs(x = "Semseter",
#        y = "Relative Ranking",
#        title = "Formative Items",
#        subtitle = "STA 215") +
#   theme(legend.position = "none") +
#   scale_color_manual(values = c("#0072B2", "#E69F00"))

```

- How can I make STA 215 material seem more relevant/useful? 
  Would like to include time to have students work on a project, but would need to think of what material could be re-positioned.
  Would allow for students/teams to be able to express themselves if this is student-driven.
  

```{r sta216-bump, cache = TRUE}
sta216_formative_items <- tribble(
  ~Item,	~F18_S01,	~F18_S03, ~F18_S05, ~W19_S01, ~W19_S02,
"Course Organization was:",	4,	3,	7,	5,	3,
"Explanations by instructor were:",	8,	16,	12,	12,	7,
"Instructor's ability to present alternative explanations when needed was:",	10,	13,	5,	13,	6,
"Instructor's use of examples and illustrations was:",	16,	12,	13,	16,	11,
"Quality of questions or problems raised by the instructor was:",	7,	10,	16,	7,	10,
"Student confidence in instructor's knowledge was:",	3,	4,	6,	14,	9,
"Instructor's enthusiasm was:",	5,	2,	2,	1,	8,
"Encouragement given students to express themselves was:",	14,	5,	8,	6,	2,
"Answers to student questions were:",	9,	17,	17,	15,	5,
"Availability of extra help when needed was:",	1,	15,	1,	3,	1,
"Use of class time was:",	12,	6,	3,	8,	17,
"Instructor's interest in whether students learned was:",	17,	9,	14,	11,	14,
"Amount you learned in the course was:",	15,	14,	11,	17,	15,
"Relevance and usefulness of course content were:",	13,	7,	15,	4,	12,
"Evaluative and grading techniques (test, papers, projects, etc.) were:",	11,	11,	9,	10,	13,
"Reasonableness of assigned work was:",	2,	8,	10,	9,	16,
"Clarity of student responsibilities and requirements was:",	6,	1,	4,	2,	4,
)

sta216_formative_items <- sta216_formative_items %>% 
  mutate(blank = NA)

sta216_formative_items_long <- sta216_formative_items %>% 
  mutate(Item = factor(Item, levels = sta216_formative_items$Item)) %>% 
  pivot_longer(cols = -Item, names_to = "Semester", values_to = "Ranking") %>% 
  mutate(Semester = factor(Semester, levels = c("F18_S01", "F18_S03", "F18_S05", "W19_S01", "W19_S02")),
         Bottom = if_else(Ranking > 10, "Yes", "No"))

sta216_formative_items_long %>%
  ggplot(aes(x = as.numeric(Semester), y = Ranking, group = Item, color = Item, label = Item)) +
  geom_bump(size = 2, alpha = 0.3) +
  scale_y_reverse(breaks = 1:17, labels = 1:17) +
  geom_bump(data = sta216_formative_items_long %>% filter(Ranking > 10),
            aes(x = as.numeric(Semester), y = Ranking, group = Item, color = Item),
            size = 2, inherit.aes = FALSE) +
  geom_text(sta216_formative_items_long %>% filter(Semester == "W19_S02"), 
            mapping = aes(x = as.numeric(Semester) + 0.1, y = Ranking), hjust = 0) +
  scale_x_continuous(breaks = 1:(length(levels(sta216_formative_items_long$Semester))+1),
                     labels = c(levels(sta216_formative_items_long$Semester),""),
                     expand = c(0,0.05),
                     limits = c(1, 12)) +
  theme_classic() + 
  labs(x = "Semester",
       y = "Relative Ranking",
       title = "Formative Items",
       subtitle = "STA 216") +
  theme(legend.position = "none")

# sta216_formative_items_long %>% 
#   ggplot(aes(x = as.numeric(Semester), y = -Ranking, group = Item, label = Item, color = Bottom)) + 
#   geom_line() +
#   geom_text(sta216_formative_items_long %>% filter(Semester == "W19_S02"), 
#             mapping = aes(x = as.numeric(Semester) + 0.1, y = -Ranking), hjust = 0) +
#   scale_x_continuous(breaks = 1:6,
#                      labels = c(levels(sta216_formative_items_long$Semester),""),
#                      expand = c(0,0.05),
#                      limits = c(1, 16)) +
#   scale_y_continuous(breaks = -1:-17,
#                      labels = 1:17) +
#   theme_classic() + 
#   labs(x = "Semseter",
#        y = "Relative Ranking",
#        title = "Formative Items",
#        subtitle = "STA 216") +
#   theme(legend.position = "none") +
#   scale_color_manual(values = c("#0072B2", "#E69F00"))
```







```{r sta321-bump, cache = TRUE}
sta321_formative_items <- tribble(
  ~Item,	~W19,
"Course Organization was:",	17,
"Explanations by instructor were:",	4,
"Instructor's ability to present alternative explanations when needed was:",	8,
"Instructor's use of examples and illustrations was:",	12,
"Quality of questions or problems raised by the instructor was:",	11,
"Student confidence in instructor's knowledge was:",	10,
"Instructor's enthusiasm was:",	2,
"Encouragement given students to express themselves was:",	3,
"Answers to student questions were:",	9,
"Availability of extra help when needed was:",	5,
"Use of class time was:",	14,
"Instructor's interest in whether students learned was:",	6,
"Amount you learned in the course was:",	7,
"Relevance and usefulness of course content were:",	1,
"Evaluative and grading techniques (test, papers, projects, etc.) were:",	13,
"Reasonableness of assigned work was:",	15,
"Clarity of student responsibilities and requirements was:",	16,
)

sta321_formative_items <- sta321_formative_items %>% 
  mutate(blank = NA)

sta321_formative_items_long <- sta321_formative_items %>% 
  mutate(Item = factor(Item, levels = sta321_formative_items$Item)) %>% 
  pivot_longer(cols = -Item, names_to = "Semester", values_to = "Ranking") %>% 
  mutate(Semester = factor(Semester, levels = c("W19")),
         Bottom = if_else(Ranking > 10, "Yes", "No"))

sta321_formative_items_long %>%
  ggplot(aes(x = as.numeric(Semester), y = Ranking, group = Item, color = Item, label = Item)) +
  geom_point(size = 2, alpha = 0.3) +
  scale_y_reverse(breaks = 1:17, labels = 1:17) +
  geom_point(data = sta321_formative_items_long %>% filter(Ranking > 10),
            aes(x = as.numeric(Semester), y = Ranking, group = Item, color = Item),
            size = 2, inherit.aes = FALSE) +
  geom_text(sta321_formative_items_long %>% filter(Semester == "W19"), 
            mapping = aes(x = as.numeric(Semester) + 0.1, y = Ranking), hjust = 0) +
  scale_x_continuous(breaks = 1:(length(levels(sta321_formative_items_long$Semester))+1),
                     labels = c(levels(sta321_formative_items_long$Semester),""),
                     expand = c(0,0.05),
                     limits = c(1, 12)) +
  theme_classic() + 
  labs(x = "Semester",
       y = "Relative Ranking",
       title = "Formative Items",
       subtitle = "STA 321") +
  theme(legend.position = "none")

# sta321_formative_items_long %>% 
#   ggplot(aes(x = as.numeric(Semester), y = -Ranking, label = Item, color = Bottom)) + 
#   geom_point() +
#   geom_text(sta321_formative_items_long %>% filter(Semester == "W19"), 
#             mapping = aes(x = as.numeric(Semester) + 0.1, y = -Ranking), hjust = 0) +
#   scale_x_continuous(breaks = 1:2,
#                      labels = c(levels(sta321_formative_items_long$Semester),""),
#                      expand = c(0,0.05),
#                      limits = c(1, 1.5)) +
#   scale_y_continuous(breaks = -1:-17,
#                      labels = 1:17) +
#   theme_classic() + 
#   labs(x = "Semseter",
#        y = "Relative Ranking",
#        title = "Formative Items",
#        subtitle = "STA 321") +
#   theme(legend.position = "none") +
#   scale_color_manual(values = c("#0072B2", "#E69F00"))
```

- There is a lot of restructuring that I would like to do with STA 321 and this was my first attempt at implementing a revision/submission policy.

```{r sta418-bump, cache = TRUE}
sta418_formative_items <- tribble(
  ~Item,	~F19_S01, ~F19_S02,
"Course Organization was:",	4,	5,
"Explanations by instructor were:",	16,	9,
"Instructor's ability to present alternative explanations when needed was:",	6,	6,
"Instructor's use of examples and illustrations was:",	8,	16,
"Quality of questions or problems raised by the instructor was:",	14,	14,
"Student confidence in instructor's knowledge was:",	5,	11,
"Instructor's enthusiasm was:",	7,	3,
"Encouragement given students to express themselves was:",	2,	1,
"Answers to student questions were:",	13,	13,
"Availability of extra help when needed was:",	9,	7,
"Use of class time was:",	11,	12,
"Instructor's interest in whether students learned was:",	12,	10,
"Amount you learned in the course was:",	3,	4,
"Relevance and usefulness of course content were:",	1,	2,
"Evaluative and grading techniques (test, papers, projects, etc.) were:",	15,	8,
"Reasonableness of assigned work was:",	17,	17,
"Clarity of student responsibilities and requirements was:",	10,	15,

)

sta418_formative_items <- sta418_formative_items %>% 
  mutate(blank = NA)

sta418_formative_items_long <- sta418_formative_items %>% 
  mutate(Item = factor(Item, levels = sta418_formative_items$Item)) %>% 
  pivot_longer(cols = -Item, names_to = "Semester", values_to = "Ranking") %>% 
  mutate(Semester = factor(Semester, levels = c("F19_S01","F19_S02")),
         Bottom = if_else(Ranking > 10, "Yes", "No"))

sta418_formative_items_long %>%
  ggplot(aes(x = as.numeric(Semester), y = Ranking, group = Item, color = Item, label = Item)) +
  geom_bump(size = 2, alpha = 0.3) +
  scale_y_reverse(breaks = 1:17, labels = 1:17) +
  geom_bump(data = sta418_formative_items_long %>% filter(Ranking > 10),
            aes(x = as.numeric(Semester), y = Ranking, group = Item, color = Item),
            size = 2, inherit.aes = FALSE) +
  geom_text(sta418_formative_items_long %>% filter(Semester == "F19_S02"), 
            mapping = aes(x = as.numeric(Semester) + 0.1, y = Ranking), hjust = 0) +
  scale_x_continuous(breaks = 1:(length(levels(sta418_formative_items_long$Semester))+1),
                     labels = c(levels(sta418_formative_items_long$Semester),""),
                     expand = c(0, 0.05),
                     limits = c(1, 12)) +
  theme_classic() + 
  labs(x = "Semester",
       y = "Relative Ranking",
       title = "Formative Items",
       subtitle = "STA 418/518") +
  theme(legend.position = "none")


# sta418_formative_items_long %>% 
#   ggplot(aes(x = as.numeric(Semester), y = -Ranking, group = Item, label = Item, color = Bottom)) + 
#   geom_line() +
#   geom_text(sta418_formative_items_long %>% filter(Semester == "F19_S02"), 
#             mapping = aes(x = as.numeric(Semester) + 0.1, y = -Ranking), hjust = 0) +
#   scale_x_continuous(breaks = 1:3,
#                      labels = c(levels(sta418_formative_items_long$Semester),""),
#                      expand = c(0,0.05),
#                      limits = c(1, 10)) +
#   scale_y_continuous(breaks = -1:-17,
#                      labels = 1:17) +
#   theme_classic() + 
#   labs(x = "Semseter",
#        y = "Relative Ranking",
#        title = "Formative Items",
#        subtitle = "STA 418/518") +
#   theme(legend.position = "none") +
#   scale_color_manual(values = c("#0072B2", "#E69F00"))
```

Work at Husson

- Taught 4/4 load along with one online 7-week course after developing during the first 7-weeks. Online courses were overload.


### Classroom management skills

### Preparation and organization

### Communication

### Enthusiasm

### Knowledge

### Evaluation

### Availability

### Intellectual motivation

### Flexibility and resourcefulness in teaching

### Dedication to students

## Scholarly activity

- Working with students on scholarly activity... I am working on developing a general "syllabus" or "contract" to share with students that are interested in working together on projects so that we have clear expectations of each other.
- List ongoing projects and specific areas that students can work with me on my personal site.
- Learning how to prioritize scholarly activities and when to encourage people to reach out to colleagues.

Work at Husson
- Consulting work with Dr. Jay Polsgrove
- Institutional research assistance

### Activities expected each year

### Activities expected periodically

### Activities that represent areas of significant focus

## Service

Work at Husson

- Developed Data Analytics undergraduate program and certificate. The underlying them for this program was to give students a solid foundation in understanding, explore, and modeling data; having students extend this foundation with more advanced concepts in computing, mathematics, or statistics; apply their skills in a domain outside of computing, mathematics, or statistics; and learning multiple ways to communicate information effectively.
- For this program, I developed DA 210 Introduction to Data Analytics, DA 310 Data Visualization (now DA 110 Data Exploration and Visualization), DA 420 Data Analytics Seminar, DA 449 Data Analytics Internship (now DA 499 Data Analytics Internship), DA 489 Data Analytics Capstone, MS 212 Intermediate Applied Statistics, and MS 332 Statistical Modeling (now MS 333 Statistical Modeling). Aided in the redevelopment of MS 181 Calculus I, MS 182 Calculus II, and MS 241 Linear Algebra with Applications.
- In preparing this program and certificate I also developed MS 132 Probability and Statistics, DA 210, and DA 310 for online 7-week delivery.
- Involved a lot of networking, traveling to local highschoolers to promote Husson and the program, traveled to a weekend high school math competition to promote program, connected with existing programs on campus to see how the DA certificate could pair with their courses load and what courses they currently offered that could satisfy domain area electives.
- Search committee member for DA new-hire and student experience coordinator.

### Activities expected each year

### Activities expected periodically

### Activities that represent areas of significant focus

## Appendices

### 

